Deep Reinforcement Learning for Conservation Decisions

### 2022-01-31 manuscript/manuscript.Rmd

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
nocite: |
    @A2C, @trpo, @ddpg, @TD3, @impala, @hafner_learning_2019, @weber_imagination-augmented_2018
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
#  - \usepackage{lineno}
#  - \usepackage{endfloat}
#  - \linenumbers

@@

\begin{table}
\begin{tabular}{l l }
\hline
Practical Challenges with Deep RL & Description   \\
\hline
   Generalization                   & blah blah  \\
   Intransparency                   & blah blah \\
   Hyperparameter Instability       & blah blah  \\
   Reward Misspecification          & blah blah \\
   Capital Intensive                & blah blah  \\
   Sample Inefficiency              & blah blah \\

\hline
\end{tabular}
\caption{Survey of common deep RL Challenges.}
\end{table}

>>>>

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
nocite: |
    @A2C, @trpo, @ddpg, @TD3, @impala, @hafner_learning_2019, @weber_imagination-augmented_2018, @kirk_survey_2022
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
#  - \usepackage{lineno}
#  - \usepackage{endfloat}
#  - \linenumbers

@@

\begin{table}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{p{5 cm} p{10 cm}}
\hline
Issue & Description   \\
\hline
   Generalization                   & Agents struggle to adapt to tasks not seen in training (Kirk et al. 2022).   \\
   Reproducibility                  & It can be very challenging to replicate results due to a host of reasons like differences in computational hardware (Henderson et al. 2019). \\
   Lack of Transparency             & Deep RL users cannot interpret why agents select actions (Castelvecchi 2016). \\
   Hyperparameter Instability       & Agent performance can vary significantly over slight alterations in hyperparameters, like initialization seed (Henderson et al. 2019).   \\
   Reward Misspecification          & Agents commonly learn undesirable behavior that still maximizes the RL objective  (Hadfield-Menell et al. 2020). \\
   High Capital Demands            & Landmark successes like AlphaGo and AlphaStar have required very large teams of researchers and large amounts of computational power (Silver et al. 2017; Vinyals et al. 2019).  \\
   Sample Inefficiency              & Current algorithms require large amounts of interaction with the environment to achieve reward maximization (Haarnoja et al. 2018).  \\

\hline
\end{tabular}
\caption{Practical issues with deep RL.}
\end{table}
